% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 


\begin{document}
	
	\name{Gyanasekaran Radhakrishnan}
	% \address used twice to have two lines of address
	\address{2050 Southwest Expressway, Apt 82, San Jose, CA 95126}
	\address{gnanesh.che@gmail.com $\mid$ (864) 633-9988}
	
	
	\begin{resume}
		
		
		\section{EDUCATION} 
		{\sl MS,} Computer Science \\
		% \sl will be bold italic in New Century Schoolbook (or
		% any postscript font) and just slanted in
		% Computer Modern (default) font
		Clemson University, Clemson, SC. 
		May 2014.\\\\
		{\sl Bachelor of Engineering,} Computer Science and Engineering \\
		% \sl will be bold italic in New Century Schoolbook (or
		% any postscript font) and just slanted in
		% Computer Modern (default) font
		Anna University, India.
		June 2007.
		
		
		\section{TECHNICAL \\ SKILLS} {\sl Languages:} Java, Python, C, C++.\\
		{\sl Mobile Development:} Android. \\
		{\sl Web \& Back-end Development:} J2EE, Web Services, Spring, Struts, Javascript. \\
		{\sl RDBMS:} MySQL, Oracle, PostgreSQL. \\
		{\sl Big Data, NoSQL:} Apache Hadoop, Lucene, Solr, RabbitMQ, MongoDB, Storm, Redis. \\
		{\sl Other Tools:} Maven, SVN, Git. \\
		{\sl Operating Systems:}  Unix/Linux, Windows, MacOS.
		
		\section{INDUSTRY EXPERIENCE} 
		{\sl Software Engineer} \hfill July 2014 - present.\\
		EBay Inc, San Jose, CA
		\begin{itemize}  \itemsep -2pt % reduce space between items
			\item Responsible for design, development of live auctions backend services using ReST, Spring and Java.
			\item Research and implement monitoring solutions using map-reduce and elasticsearch. 
		\end{itemize}
		{\sl Technical Intern PhD} \hfill Summer 2013\\
		EBay Inc, San Jose, CA
		\begin{itemize}  \itemsep -2pt % reduce space between items
			\item Built a tag mining system using topic mining algorithms.
			\item Improved quality of tags by 99.1\% as compared with raw \emph{ngrams}.
			\item \emph{Tools Used: Apache Hadoop, MongoDB, Apache Lucene and Apache Solr.}
		\end{itemize}
		{\sl Application Engineer} \hfill 2010-2011 \\
		Oracle, 
		Bangalore, India
		\begin{itemize}  \itemsep -2pt % reduce space between items
			\item Extended Oracle Fusion CRM Sales functionality to mobile.
			\item Implemented location/context based features specific to mobile sales.
		\end{itemize}
		{\sl Android Developer} \hfill            2009-2010 \\
		MySpace (representing Aditi Technologies) 
		\begin{itemize}  \itemsep -2pt %reduce space between items
			\item Developed the Official MySpace Android application - one of the first 14 apps to hit Android market.
			\item Improved performance of individual pages and overall application using AIDL
			remote services.
			\item Developed Oauth security layer that is used to form requests from the Android application. 
			\item Implemented and consumed Long Polling in the MySpace mobile application for alerts.
		\end{itemize} 
		{\sl Senior Development Engineer} \hfill        2007-2010 \& 2011 \\
		Aditi Technologies, Bangalore, India.
		\begin{itemize}
			\item Responsible for design and development of web backend(J2EE) and mobile(Android) applications.
			\item Incorporated clustering and load balancing algorithms for content management systems.
			\item Responsible for performance tuning in production web applications that scaled the application to support 10,000 concurrent users - a 400\% increase.
		\end{itemize} 
		
		
		\section{ACADEMIC \\ PROJECTS}  {\sl Data Mining} \hfill        C++
		\begin{itemize}  \itemsep -2pt %reduce space between items
			\item Implemented a music recommender system using Collaborative Filtering for Yahoo music dataset.
			\item Improved running time efficiency of SVD feature toolkit but performing user grouping in the dataset prior to matrix factorization.
		\end{itemize} 
		{\sl Object-Oriented Game Design}  \hfill        C++
		\begin{itemize} \itemsep -2pt
			\item Designed and developed KReversi/Othello - a 2D board game.
			\item Implemented greedy and divide-and-conquer algorithms for AI.
			\item Tools: Valgrind.
		\end{itemize} 
		{\sl Compiler Design}  \hfill        Python
		\begin{itemize} \itemsep -2pt
			\item Designed and developed a compiler from scratch for a basic imperative language.
			\item The grammar uses a weak precedence parser.       
		\end{itemize}
		
		\section{RESEARCH}	\begin{itemize}  \itemsep -2pt
			\item Conducted research in data management of sensor data in structured(Relational), semi-structured(Semantically-annotated) and unstructured(Raw) formats. 
			\item Enabled real-time processing of sensor observation data and sensor diagnostics data using semantic web and linked data technologies such as SPARQL, C-SPARQL and Apache Jena with focus on scalability.
			\item \emph{Tools/technologies: RabbitMQ for data transport, Redis for caching, MongoDB for raw data archiving and Storm for enabling multi-tenancy.}
		\end{itemize}
		
		\section{ACADEMIC EXPERIENCE}  {\sl Graduate Research Assistant} \hfill        Intelligent River\textsuperscript{\textregistered} Project
		\begin{itemize}  \itemsep -2pt
			\item Working on distributed, scalable solutions for real- time monitoring, analysis and management of water resources using Semantic Web and Linked Data principles.
		\end{itemize}
		
		{\sl Graduate Research Assistant} \hfill        Exascale Filesystem Project
		\begin{itemize}  \itemsep -2pt
			\item Conducted research on Digital Rights Management(DRM) for security in parallel and distributed filesystems. Specific research was done pertaining to Authentication and Authorization in distributed filesystems using OASIS standards.
		\end{itemize}
		
		{\sl Graduate Teaching Assistant} \hfill        Fall 2011
		\begin{itemize}  \itemsep -2pt
			\item Taught C programming lab sessions for multiple sections of undergraduates.
		\end{itemize}
		
		
		\section{AWARDS \& \\ ACHIEVEMENTS}
		\begin{itemize}  \itemsep -2pt             
			\item Finalist - top 8 out of 109 teams in {\it AngelHack Silicon Valley} , Summer 2013.
			\begin{itemize}  \itemsep -4pt 
				\item Built a drone using ardupilot and a created a drone data management system for tracking drones.
			\end{itemize}
			\item Won {\it SPARC-EDGE Hackathon} at Charleston, SC, August 2011.
			\begin{itemize}  \itemsep -4pt 
				\item Won joint first prize out of 30+ teams by building an Android app called ParkingPal that uses computer vision to help park and find parked cars.
			\end{itemize}
			\item Awarded {\it Research and Teaching Assistantship} by School of Computing, Clemson University.
		\end{itemize}
	\end{resume}
\end{document}
